Paper without a name

### 2014-06-01 Article.tex
Translate intuition ; integrate to article.

>>>>

\subsection{Explaining our intuition}

We work here with $n = 2^p$ wires. Our idea is that we need to be able to route
any of the $n$ input wires to any of the $n$ output wires. A box enables the
{\em swapping} or {\em non-swapping} of two wires. Its behaviour is tightly
linked with that of the two wires.

We tried to imagine a step of {\em multiplexing} followed by a step of {\em
demultiplexing}, that would regroup all the wires in one point before deciding
which wire goes where. Since one box is plugged on two wires, we can imagine its
output as being one bus of two wires. The idea is thus relatively simple :

\begin{itemize}
	\item We begin with $n = 2^p$ simple wires
	\item We group them two by two into $2^{p-1}$ buses of size $2$
	\item We group the buses two by two into $2^{p-1}$ buses of size $4$
	\item \dots
	\item We group the two buses of size $2^{p-1}$ into one bus of size $2^p$.
\end{itemize}

Now the demultiplexing step is just the opposite :

\begin{itemize}
	\item We begin with one bus of $2^p$ wires that we separate into two smaller
	buses of $2^{p-1}$ wires
	\item \dots
	\item We separate the $2^{p-1}$ buses of 2 wires into $2^p$ simple wires.
\end{itemize}

The grouping/separation of wires requires a given number of boxes, and we tried
to put just that number of boxes in the box system we designed. Grouping two
buses of $k$ wires requires $k$ boxes.

We tried this box system and found, for small values of $n$, that it worked.

\subsubsection{Number of boxes}

Let $n = 2^p$ be the number of wires. On each line of grouping/separating we
have $n/2$ boxes. We now need to count lines of grouping and of separating. We
begin from $n=2^p$ wires and want to group them into 1 bus, therefore we need
$p$ lines of grouping. Conversely, we then need to separate one bus into $2^p$
wires, therefore requiring $p$ lines of separating.

We notice that the last line of grouping and the first line of separating have
exactly the same boxes and each wires is used by exactly one grouping box and
one separating box. These two lines are thus redundant and we only put one of
them.

Finally :

$$\begin{array}{l l l}
	\# \mathrm{boxes} &=& \# \mathrm{boxes per line} \times \left(
			\# \mathrm{group lines} + \# \mathrm{separate lines} - 1
			\right) \\
		&=& \frac{n}{2} (2 p - 1) \\
		&=& n ^ {p - 1/2} \\
		&=& n ^ {log_2 n - 1/2}
\end{array}$$
